NLIZE: A Perturbation-Driven Visual Interrogation Tool for Analyzing and Interpreting Natural Language Inference Models: Supplementary Materials

### 2018-03-31 paper/background.tex
space squeeze
update figures
update teaser
add open source comment add title to the appendix

\begin{table}[htbp]
\label{tab:NLI}
\centering
\caption{An illustration of natural language inference.}
 \begin{tabular}{c | c c c c}
 \hline
  P / H & sentences & entail & contradict & neutral \\ [0.5ex]
 \hline
 premise & Boy ate an apple. &  -  &  -  & - \\
 hypothesis & Kid ate fruits. & \checkmark &   &  \\
 hypothesis & Boy ate a banana. &  & \checkmark & \\
 hypothesis & Tom ate an apple. &  &  & \checkmark \\
 hypothesis & Boy ate a Fuji apple. &   &  & \checkmark \\
 %\hline
 %premise & Facebook's IPO electrified the general public. &  -  &  -  & - \\
 %hypothesis & Facebook went public. & \checkmark   &  &  \\
 %hypothesis & General Electric went public. &  &   & \checkmark \\
 %hypothesis & People ignored Facebook's IPO. &  & \checkmark & \\
 \hline
\end{tabular}
\end{table}

At first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation; however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
%
Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from the learning algorithm's point of view). Take the following sentences as an example (here \textbf{P} refers to premise, \textbf{H} refers to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO. The literal similarity between ``Electric'' and ``electrified'' may trick a model to predict \textbf{H2} as \emph{entailment}. A model likely will also fail to understand the link between ``went public'' and ``IPO'', and therefore, mistake \textbf{H1} as \emph{neutral}.
%
%The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
%deep comprehension of textual information. Major tasks include Natural Language Inference,
%Machine Translation, Questions Answering, Summarization, and etc.
%Recently, neural networks models have performed strongly on these tasks.
%
Recently, Bowman et al. introduced a large corpus~\cite{BowmanAngeliPotts2015} for NLI tasks, which has helped spawn a new wave of effective neural network models for those tasks. Here, we focus on the analysis of the decomposable attention model~\cite{parikh2016emnlp} on this dataset.

@@

\begin{figure}[htbp]
\centering
 \includegraphics[width=1.0\linewidth]{end2end}
 \vspace{-2mm}
 \caption{End-to-end NLP neural network model.}
  \vspace{-2mm}
\label{fig:modelPipeline}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.9\linewidth]{attentionIllustration}

 \caption{Attention can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks. On the left, the matrix shows the attention between between premise and hypothesis pair. On the right, attention can also be interpreted as alignment.}
\label{fig:attention}
\end{figure}

>>>>

\begin{table}[htbp]
\vspace{-2mm}
\label{tab:NLI}
\centering
\caption{An illustration of natural language inference.}
 \begin{tabular}{c | c c c c}
 \hline
  P / H & sentences & entail & contradict & neutral \\ [0.5ex]
 \hline
 premise & Boy ate an apple. &  -  &  -  & - \\
 hypothesis & Kid ate fruits. & \checkmark &   &  \\
 hypothesis & Boy ate a banana. &  & \checkmark & \\
 hypothesis & Tom ate an apple. &  &  & \checkmark \\
 hypothesis & Boy ate a Fuji apple. &   &  & \checkmark \\
 %\hline
 %premise & Facebook's IPO electrified the general public. &  -  &  -  & - \\
 %hypothesis & Facebook went public. & \checkmark   &  &  \\
 %hypothesis & General Electric went public. &  &   & \checkmark \\
 %hypothesis & People ignored Facebook's IPO. &  & \checkmark & \\
 \hline
\end{tabular}
\vspace{-2mm}
\end{table}

At first glance, the task of natural language inference may seem less practical compared to other well-known NLP challenges such as machine translation; however, the ability to distinguish entailment and contradiction relationship is fundamental to understanding natural language at large.
%
Considering the ambiguousness of natural language and polysemy words, the inference task can become quite challenging (especially from the learning algorithm's point of view). Take the following sentences as an example (here \textbf{P} refers to premise, \textbf{H} refers to hypothesis):  (\textbf{P}) Facebook's IPO electrified the general public; (\textbf{H1}) Facebook went public; (\textbf{H2}) General Electric went public; (\textbf{H3}) People ignored Facebook's IPO. The literal similarity between ``Electric'' and ``electrified'' may trick a model to predict \textbf{H2} as \emph{entailment}. A model likely will also fail to understand the link between ``went public'' and ``IPO'', and therefore, mistake \textbf{H1} as \emph{neutral}.
%
%The grand challenge in Natural Language Processing (NLP) is to have machine to acquire
%deep comprehension of textual information. Major tasks include Natural Language Inference,
%Machine Translation, Questions Answering, Summarization, and etc.
%Recently, neural networks models have performed strongly on these tasks.
%
Recently, Bowman et al. introduced a large corpus~\cite{BowmanAngeliPotts2015} for NLI tasks, which has helped spawn a new wave of effective neural network models for those tasks. Here, we focus on the analysis of the decomposable attention model~\cite{parikh2016emnlp} on this dataset (see \textbf{Appendix A} for a detailed description of the model).

@@

\begin{figure}[htbp]
\vspace{-2mm}
\centering
 \includegraphics[width=1.0\linewidth]{end2end}
 \vspace{-5mm}
 \caption{The shared structure of end-to-end NLP neural network models.}
  \vspace{-2mm}
\label{fig:modelPipeline}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\vspace{-2mm}
 \includegraphics[width=0.85\linewidth]{attentionIllustration}
  \vspace{-2mm}
 \caption{Attention can be naturally explained as a form of alignment which exposes an interpretable layer in end-to-end neural networks. On the left, the matrix shows the attention between between premise and hypothesis pair. On the right, attention can also be interpreted as alignment.}
\label{fig:attention}
  \vspace{-2mm}
\end{figure}
